Supplmental Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-02-01 Ben_Manuscripts/structure_paper/supplemental.tex
New figures and edits

>>>>

  \noindent
  \begingroup
        \fontsize{14pt}{14pt}\selectfont
        \textbf{Crosslinking Mechanism}
  \endgroup

  Crosslinking of the the monomer Na-GA3C11 occurs by a UV initiated free
  radical polymerization (Figure~\ref{fig:xlink_mech}).  Head-to-tail addition
  takes place between terminal vinyl groups on each of the monomer tails.  We
  only considered head-to-tail addition since it is the dominant propagation mode
  in the real system.

  \begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Crosslink_mechanism.eps}
  \caption{Terminal vinyl groups present on each monomer tail react with free
	  radical initiators to create monomers with terminal vinyl radicals.  Vinyl
	  radicals react with the vinyl groups of other monomers in to propagate
	  crosslinking.}\label{fig:xlink_mech}
  \end{figure}
